---
title: "p8105_hw5_rq2166"
author: "Ruoyuan Qian"
date: "11/2/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(ggplot2)
library(ggridges)
library(broom)
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
```

# Problem 1
```{r}
set.seed(10)
iris_with_missing = iris %>%
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```


```{r}

fill_na = function(x) {
  
  if (is.numeric(x)) {
    replace = round((mean(x, na.rm = TRUE)),2)
    x[is.na(x)] <- replace
  } else if (is.character(x)) {
    replace = "virginica"
    x[is.na(x)] <- replace
  }
  x
}

iris_with_missing_fill = map(iris_with_missing,fill_na)  
 
  filled_data = as.data.frame(iris_with_missing_fill)
  
```

# Problem 2
```{r}
name = list.files(path="./data")

 read_data = function(x){
   file_name = str_c("./data/",x)
   read_csv(file_name) %>% 
     mutate(id = str_sub(x,5,6),
            id = as.numeric(id),
            arm = str_sub(x,1,3))
                        }
```

```{r,include=FALSE}

result_list = 
  tibble(
     name   =  name,
     result = map(name,read_data)) %>% 
  unnest(result)

result_data = 
  result_list%>% 
  janitor::clean_names()%>%
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observation") %>% 
  mutate(id = str_sub(name,5,6),
         id = as.numeric(id),
         arm = str_sub(name,1,3),
         week = as.numeric(week)) %>% 
  select(id,arm,everything()) %>% 
  select(-name)

  
 
```

```{r}
result_data %>% 
  mutate( id = factor(id)) %>% 
  group_by(arm,id) %>% 
 ggplot(aes(y = observation, 
            x = week, color = id))+
  geom_line()+
  facet_grid(. ~ arm) +
  viridis::scale_color_viridis(
               discrete = TRUE )+
  theme(legend.position = "bottom")+
  labs(x = "Week",
       y = "Observation",
       title = "Plot 1   Spaghetti plot showing observations on each subject over time"
       )+
   theme(plot.title = element_text(hjust = 0.5))
```

As for the control group, the obervations of subjects generally unchanged overtime regardless of some fluctuations. However, as for the experiment group, there is an increasing trend among observations over time. 

# Porblem 3
```{r}
set.seed(1)

sim_regression = function(n = 30, beta0 = 2, beta1, mean = 1, sd = sqrt(50)) {
  
  sim_data = tibble(
    x = rnorm(n, 0, 1),
    y = beta0 + beta1 * x + rnorm(n, 0, sd)
  )
  
  ls_fit = lm(y ~ x, data = sim_data)
  
  tibble(
    beta1_hat = coef(ls_fit)[2],
    p_value = tidy(ls_fit)[[2,5]]
  )
}
```

## beta1 = 0
```{r}
sim_results = 
  tibble(beta1 = c(0)) %>% 
  mutate(
    output_lists = map(.x = beta1, ~rerun(10000, sim_regression( beta1 = .x))),
    estimate_dfs = map(output_lists, bind_rows)) %>% 
  select(-output_lists) %>% 
  unnest(estimate_dfs)
```

## beta1 = c(1:6)
```{r}
sim_results = 
  tibble(beta1 = c(1:6)) %>% 
  mutate(
    output_lists = map(.x = beta1, ~rerun(10000, sim_regression( beta1 = .x))),
    estimate_dfs = map(output_lists, bind_rows)) %>% 
  select(-output_lists) %>% 
  unnest(estimate_dfs)

```

```{r}
sim_results %>% 
  group_by(beta1) %>% 
  mutate( n = n()) %>% 
 filter(p_value < 0.05) %>% 
  mutate( n_reject_null = n(),
          power = n_reject_null/n) %>% 
  select(beta1,power) %>% 
  distinct() %>% 
 ggplot(aes(x = beta1, y = power))+
  geom_line()  +
  labs(x = "True beta1",
       y = "Power",
       title = "Plot 2   Powers across different true beta1"
       )
```

As for this situation, we can assume that the `effect size` is the difference between true beta1 and zero. As the true beta1 increases, the effect size increases as well. 

According to the Plot 2, the `power` increases when the `effect size` increases. So the association between power and effect size is `positively correlated`.

```{r}
plot_mean_all = 
sim_results %>% 
  group_by(beta1) %>% 
  mutate(mean_all = mean(beta1_hat)) %>% 
  filter(p_value < 0.05) %>% 
  mutate( mean_p = mean(beta1_hat)) %>%
  select(beta1,mean_all,mean_p) %>% 
  distinct() %>% 
  ggplot(aes(x = beta1, y = mean_all)) +
  geom_line(aes(color = "mean for all values"))+
  theme(legend.position = "bottom")+
  labs(x = "True beta1",
       y = "Mean of beta1",
       title = "Plot 3  Average estimate of beta1_hat"
       )+
  theme(plot.title = element_text(hjust = 0.5))

plot_mean_all
  
```

```{r}
plot_mean_all+
  geom_line(aes(x = beta1,  y = mean_p, color= "mean for values rejected the null" ))+
   theme(plot.title = element_text(hjust = 0.5))
```

According to Plot 3, the `true beta1` and the `average` for the tests rejected the null are not equal. They are hugely different when the effect size is small, and there is a trend that the difference will decrease when the effect size increases.

The reason is that when the effect size is small, the `power` of the test is low, so the number of the tests rejected the null is small, and the tests of beta1 rejected the null tend to be away from the null which is zero in the situation. Therefore, the `average` for the tests rejected the null tend to be larger than the `true beta1`, and the difference between them are extreme. However, as the effect size increases, the `power` increases, the number of the tests rejected the null increases. So the difference between two is increasingly small.

